---
title: "MA615_Midterm_ioSlides"
author: "Yiping Jiang"
date: "10/21/2019"
output: ioslides_presentation
---

# 0. EDA  
  
## Indicators:  

**GNI per capita (Atlas $): **   
It is the gross national income, converted to U.S. dollars using the World Bank Atlas method, divided by the midyear population.
  
**Access to electricity (% of population): **   
It is the percentage of population with access to electricity. Electrification data are collected from industry, national surveys and international sources.  
  
**Urban population (% of total population): **   
It refers to people living in urban areas as defined by national statistical offices. The data are collected and smoothed by United Nations Population Division.
  
## **Research Question: **  
Is there a correlation between GNI per capita and access to electricity? How strond is the correlation? 

And how about GNI per capita and urban population? How strong the correlation is?  
  
```{r setup, echo = F, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(WDI)
```
  
  
# 1. Get Data  
  
## HOW
```{r echo = T, include = F}
new_wdi_cache <- WDIcache()
WDIsearch("Access to electricity")
WDIsearch("Urban population")
WDIsearch("gdp.*capita.*US\\$", cache = new_wdi_cache)
```
  
# 2. Clean Up  
  
##  Dataframe Combining & Data Cleaning  
### ???
```{r echo = F}
wdi_data <- WDI(indicator = c("NY.GNP.PCAP.CD","EG.ELC.ACCS.ZS","SP.URB.TOTL.IN.ZS"), start = 1960, end = 2019, extra = TRUE)
names(wdi_data)
wdi_data <- subset(wdi_data, region != "Aggregates")
names(wdi_data)[which(names(wdi_data) == "NY.GNP.PCAP.CD")] <- "GNI"
names(wdi_data)[which(names(wdi_data) == "EG.ELC.ACCS.ZS")] <- "Electricity"
names(wdi_data)[which(names(wdi_data) == "SP.URB.TOTL.IN.ZS")] <- "Urban_Population"
data=na.omit(wdi_data)
names(data)
```

# 3. Plot Graphs
  
```{r echo = F, include = F}
pt1 = ggplot(data, aes(x = GNI)) +
  geom_histogram(bins = 100, fill="blue")
summary(data$GNI)

pt2 = ggplot(data, aes(x = Electricity)) +
  geom_histogram(bins = 20, fill="purple")
summary(data$Electricity)

pt3 = ggplot(data, aes(x = Urban_Population)) +
  geom_histogram(bins = 20, fill="darkgreen")
summary(data$Urban_Population)
```
## ??
```{r echo = F, include = T}
gridExtra::grid.arrange(pt1, pt2, pt3, ncol= 3)
```

## Data Transformation  
```{r echo = F}
develop <- data %>% 
  group_by(year) %>% 
  summarize(Electricity = mean(Electricity), Urban_Population = mean(Urban_Population), GNI = mean(GNI))
kable(develop[1:5, ], digits = 4, align = "c", booktabs = TRUE, caption = "Worldwide Development", col.names = c("Year", "Urban Population","Electricity","GNI" ))
```

## Scatter Plots
```{r echo = F}
#scatter plot of GNI per Capita:
pt4 = ggplot(data, aes(x = year, y = GNI), title = "GNI") + 
  geom_point(size = 0.1, color="red") + 
  scale_x_continuous("Year", breaks = seq(1990, 2019, 2)) + 
  geom_smooth(color="blue") 

#scatter plot of Electricity:
pt5 = ggplot(data, aes(x = year, y = Electricity), title = "Electricity") + 
  geom_point(size = 0.1, color = "orange") + 
  scale_x_continuous("Year", breaks = seq(1990, 2019, 2)) + 
  geom_smooth(color="green")  

#scatter plot of Prevalence of Urban Population:
pt6 = ggplot(data, aes(x = year, y = Urban_Population), title = "Urban_Population") +
  geom_point(size = 0.1, color = "purple") + 
  scale_x_continuous("Year", breaks = seq(1990, 2019, 2)) + 
  geom_smooth(color="black")  

gridExtra::grid.arrange(pt4, pt5, pt6, ncol= 1)
```

## Linear Regression & Correlation
```{r echo = F}
#plot Urban Population vs. GNI per Capita.
pt8 = ggplot(data, aes(x = GNI, y = Urban_Population)) + 
  geom_point(size = 1L, alpha = 0.5, colour = "#0c4c8a") + 
  geom_smooth(color= "darkred", size = 0.5) 

# square root scale of GNI
pt7 = ggplot(data) +
  aes(x = GNI, y = Electricity) +
  geom_point(size = 1L, colour = "#0c4c8a", alpha = 0.5) +
  scale_x_continuous(trans = "sqrt") +
  theme_minimal() + 
  geom_smooth(color = "darkred", size = 0.5)

gridExtra::grid.arrange(pt7, pt8, ncol= 1)
```
  
##  
### Plot Urban Population vs. GNI per Capita.

```{r echo = F}
ggplot(data, aes(x = GNI, y =Urban_Population)) + 
  geom_point(size = 1L, alpha=0.5, colour = "#0c4c8a") + 
  geom_smooth(color="darkred", size=0.5)  
```
